# HW 3&4
This notebook is created by Kaiyi Li at 2020.03.08 for the homework 3 and 4 of volatility class.
Before we get started, let's load the dataset and library.
```{r}
library(rugarch)
library(ggplot2)
library(reshape2)
raw_data <- read.table("spyxlevix20.TXT",header = T)
#Covert the date to date object
raw_data$date <- as.Date(raw_data$date)
raw_data = na.omit(raw_data)
raw_data
```
Next, we plot all these series.
```{r}
theme_set(theme_classic())
ggplot(raw_data, aes(x=date)) +
  ylab('Price')+
  geom_line(aes(y=raw_data$spy,col='SPY'),alpha=1) +
  geom_line(aes(y=raw_data$vix,col='VIX'),alpha=1) +
  geom_line(aes(y=raw_data$xle,col='XLE'),alpha=1) +
    theme(legend.position=c(.1,.85))
# ggplot2::ggsave("PricePaths.jpg")
```

## You have a portfolio of $1,000,000 of stock all in XLE which is an energy ETF. What is the 1% one day Value at Risk for this portfolio on Monday Jan 20, 2020? Use the attached dataset.
First, let's plot the path of XLE's return.
```{r}
xle_returns <- data.frame(
  date = raw_data$date[-1],
  xle_return = diff(log(raw_data$xle))
)
ggplot(xle_returns, aes(x=date)) +
  geom_line(aes(y=xle_return),group = 1,colour = "blue") +
  labs(title="Logarithmic Daily Returns of XLE",
       caption="Source: Given ",
       y="Returns")
# ggplot2::ggsave("XLE_Daily_Returns.jpg")
```
The distribution of XLE's return.
```{r}
ggplot(xle_returns,aes(x=xle_return))+
  geom_vline(aes(xintercept=mean(xle_return)),colour = "red",linetype="dashed")+geom_histogram(binwidth = 0.00125,colour = "blue")+
  geom_density(alpha=0.05, fill="#FF6666") +
  labs(
  title = "Distribution of Logarithmic Daily Returns of XLE"
)
# ggplot2::ggsave("Distribution_of_Logarithmic_Daily_Returns_of_XLE.jpg")
```

### a) Using the quantile from one year history it is?
```{r}
# Extract returns of last year.
last_year_xle_returns <- tail(xle_returns,252)
# last_year_xle_returns
ggplot(last_year_xle_returns,aes(x=xle_return))+
  geom_vline(aes(xintercept=mean(xle_return)),colour = "red",linetype="dashed")+geom_histogram(binwidth = 0.00125,colour = "blue")+
  geom_density(alpha=0.05, fill="#FF6666") +
  labs(
  title = "Distribution of Logarithmic Daily Returns of XLE of Last Year"
)
# ggplot2::ggsave("Distribution_of_Logarithmic_Daily_Returns_of_XLE_Of_Last_Year.jpg")
```

```{r}
rets <- last_year_xle_returns$xle_return
quantile(rets , 0.01)
```
```{r}
qplot(rets , geom = 'histogram') + geom_histogram(fill = 'lightblue' , bins = 30) +
    geom_histogram(aes(rets[rets < quantile(rets , 0.01)]) , fill = 'red' , bins = 30) +
    labs(x = 'Daily Returns',y='Count',caption = "Red:VaR" )
# ggplot2::ggsave("Last_Year_VaR.jpg")
```

**Using one year data, the VaR is $32129.11. **

### b) Using the quantile from the full data set it is?
```{r}
rets<- xle_returns$xle_return
quantile(rets , 0.01)
```
```{r}
qplot(rets , geom = 'histogram') + geom_histogram(fill = 'lightblue' , bins = 30) +
    geom_histogram(aes(rets[rets < quantile(rets , 0.01)]) , fill = 'red' , bins = 30) +
    labs(x = 'Daily Returns',y='Count',caption = "Red:VaR" )
# ggplot2::ggsave("Full_Dataset_Year_VaR.jpg")
```

**Using full data, the VaR is $4516.11. **

### c) Using the normality assumption and a GARCH(1,1), it is?
```{r}
garchSpec <- ugarchspec(
  variance.model=list(model="sGARCH", garchOrder=c(1,1)),
  mean.model=list(armaOrder = c(0,0),include.mean=F))
fit = ugarchfit(spec = garchSpec,data = xle_returns$xle_return)
garch_vol_pred <- ugarchforecast(fit, n.ahead = 1)
-qnorm(0.01)*sigma(garch_vol_pred)*10^6
```
**Under normality assumption, using GARCH(1,1), the VaR is $20468.25 **

### d) Using the GJR-GARCH model model with normality, it is?
```{r}
GJRgarchSpec <- ugarchspec(
  variance.model=list(model="gjrGARCH", garchOrder=c(1,1)),
  mean.model=list(armaOrder = c(0,0),include.mean=F),
  distribution.model="norm")
fit = ugarchfit(spec = GJRgarchSpec,data = xle_returns$xle_return)
GJR_garch_vol_pred <- ugarchforecast(fit, n.ahead = 1)
-qnorm(0.01)*sigma(GJR_garch_vol_pred)*10^6
```
**Under normality assumption, using GJR-GARCH(1,1), the VaR is $21697.15 **

### e) Using the GJR-GARCH model with bootstrapped residuals, it is?
```{r}
resid = xle_returns$xle_return/fit@fit$sigma
-quantile(resid,0.01)*sigma(GJR_garch_vol_pred)*10^6
```
**With bootstrap residuals, using GJR-GARCH(1,1), the VaR is $24342.48 **

## 2. Which asymmetric form of ARCH model works best for SPY, (an ETF for sp500) in the attached data set?
Plot the return path of SPY.
```{r}
spy_returns <- data.frame(
  date = raw_data$date[-1],
  spy_return = diff(log(raw_data$spy))
)
ggplot(spy_returns, aes(x=date)) +
  geom_line(aes(y=spy_return),group = 1,colour = "red") +
  labs(title="Logarithmic Daily Returns of SPY",
       caption="Source: Given ",
       y="Returns")
# ggplot2::ggsave("SPY_Daily_Returns.jpg")
```
Plot the distribution of SPY returns.
```{r}
ggplot(spy_returns,aes(x=spy_return))+
  geom_vline(aes(xintercept=mean(spy_return)),colour = "red",linetype="dashed")+geom_histogram(binwidth = 0.00125,colour = "red")+
  geom_density(alpha=0.05, fill="#FF6666") +
  labs(
  title = "Distribution of Logarithmic Daily Returns of SPY"
)
# ggplot2::ggsave("Distribution_of_Logarithmic_Daily_Returns_of_SPY.jpg")
```
### a) Compare GJR-GARCH and EGARCH with GARCH using the Schwarz criterion.
Fit the data with each model first.
```{r}

```


































