# Last Part Of Volatility Final Project: Real Life Application, Stock Price Forecasting. 

All the effort was trying to get a gauk on how to estimate the parameter of GARCH(1,1). Now we go for the real life application. 


Load the data.
```{r}
gspc <- read.csv("GSPC.csv")
gspc <- data.frame(
  DATE = as.Date.factor(gspc$Date),
  Price = gspc$Close
)
vix <- read.csv("VIX.csv")
vix <- data.frame(
  DATE = as.Date.factor(vix$Date),
  VIX = vix$Close
)
```

Plot the price paths for S&P500 and VIX.
```{r}
library(ggplot2)
library(dplyr)
theme_set(theme_classic())
ggplot(gspc, aes(x=DATE, y=Price)) +
  geom_line() + 
  labs(title="S&P 500 Path",
       caption="Source: Yahoo Finance",
       y="Price")
ggplot2::ggsave("GSPCPath.jpg")
```
```{r}
ggplot(vix, aes(x=DATE, y=VIX)) +
  geom_line() + 
  labs(title="CBOE Volatility",
       caption="Source: Yahoo Finance",
       y="VIX index")
ggplot2::ggsave("VIXPath.jpg")
```
Then we plot the returns of S&P 500.
```{r}
daily_returns <- data.frame(
  Date = gspc$DATE[-1],
  Returns = diff(log(gspc$Price))
)
ggplot(daily_returns, aes(x=Date)) +
  geom_line(aes(y=Returns),group = 1,colour = "blue") +
  labs(title="Logarithmic Daily Returns of S&P500",
       caption="Source: Yahoo Finance ",
       y="Returns")
ggplot2::ggsave("GSPCReturnPath.jpg")
```

We have done this before in HW3&4, we believe GJR-GARCH(1,1) is a better fit for S&P 500. Note that the fit mechanism for GJR GARCH is also MLE.
```{r}
library(rugarch)
GJRgarchSpec <- ugarchspec(
  variance.model=list(model="gjrGARCH", garchOrder=c(1,1)),
  mean.model=list(armaOrder = c(0,0),include.mean=F),
  distribution.model="norm")
GJR_fit <- ugarchfit(
  spec = GJRgarchSpec,
  data = daily_returns$Returns
)
# GJR_fit
```
Then we plot the GJR fitted volatility as a comparison to VIX.
```{r}
annualized_GJR_vol <- 100*GJR_fit@fit$sigma*sqrt(252)
#Join series.
join_vols <- data.frame(
  GJR_vols = annualized_GJR_vol,
  vix = vix$VIX[-1],
  date = vix$DATE[-1]
)
ggplot(join_vols, aes(x=date)) +
  ylab('Volatility')+
  geom_line(aes(y=join_vols$vix,color='VIX'),alpha=1)+
  geom_line(aes(y= join_vols$GJR_vols,col='GJR'),alpha=1)+
  scale_color_manual(name = "Variables",
                     values = c("VIX" = "red", "GJR" = "blue"))
    theme(legend.position=c(.1,.85))
ggplot2::ggsave("volatilities.jpg")
```
Now we start our forecast using GJR:
```{r}
forc = ugarchforecast(GJR_fit, n.ahead=30)
```

```{r}
forecasted_sigmas <- c(unclass(sigma(forc))[,"1990-11-08 08:00:00"][1:30])
forescasted_and_estimated <- c(GJR_fit@fit$sigma,forecasted_sigmas)
date <- daily_returns$Date
horizon <- seq.Date(as.Date(date[length(date)])+1, length.out = 30, by = "day")
horizon <- c(as.Date(date)[-1],horizon)
combined_daily_data <- data.frame(
  Date = horizon,
  volatilities = forescasted_and_estimated[-1],
  col = c(rep("blue", 7615), rep("red", 30))
)
ggplot(combined_daily_data, aes(x=Date, y=volatilities)) +
  geom_line(aes(colour=col, group=1)) +
  scale_colour_identity()+
  labs(
    title = "Estimate and Predicted Daily Volatility",
    caption = "Yellow: Estimates, Green: Predicted"
  )
ggplot2::ggsave("EstimateAndPredictedDailyVolatility.jpg")
```

Then we plot the return forecasted.
```{r}
forecasted_returns <- forecasted_sigmas*rnorm(1)
forescasted_and_historical <- c(daily_returns$Returns,forecasted_returns)
# horizon <- seq.Date(as.Date(date[length(date)])+1, length.out = 30, by = "day")
# horizon <- c(as.Date(date)[-1],horizon)
combined_return_daily_data <- data.frame(
  Date = horizon,
  returns = forescasted_and_historical[-1],
  col = c(rep("blue", 7615), rep("red", 30))
)
ggplot(combined_return_daily_data, aes(x=Date, y=returns)) +
  geom_line(aes(colour=col, group=1)) +
  scale_colour_identity()+
  labs(
    title = "Historical and Predicted Daily Return",
    caption = "Blue: Historical Returns, Red: Predicted"
  )
ggplot2::ggsave("HistoricalAndPredictedDailyReturn.jpg")
```

Calculate the predicted stock price given return.
```{r}
Predicted_Horizon <- seq.Date(as.Date(date[length(date)])+1, length.out = 30, by = "day")
last_historical_price <- tail(gspc,1)$Price
```


```{r}
last_historical_price <- tail(gspc,1)$Price
forecasted_prices <- c(last_historical_price)
for (i in 1:length(forecasted_returns)) {
  predict_price <- forecasted_prices[i]*(1+forecasted_returns)
  # predict_price <- forecasted_prices[i]*log(1+forecasted_returns)
  forecasted_prices <- c(forecasted_prices,predict_price)
}
predicted_stock_price_path <- data.frame(
  Date = Predicted_Horizon,
  prediction = forecasted_prices[-1]
)
# predicted_stock_price_path
ggplot(predicted_stock_price_path, aes(x=Date, y=prediction)) +
  geom_line() + 
  labs(title="S&P 500 Path",
       caption="Source: Forcasted",
       y="Price")
ggplot2::ggsave("Predicetd_Path.jpg")
```



Bayes GARCH(1,1) Estimation

```{r}
# library(bayesGARCH)
# simulation_result <- read.csv("simulation_result.csv")
# y <- simulation_result$r
# MCMC <- bayesGARCH(y, lambda = 100, delta = 500,
# control = list(n.chain = 2, l.chain = 200))
# jpeg('mcmc.jpg')
# plot(MCMC)
# dev.off()
```



